cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-11-28 paper-cardinalR.Rmd
Updated trefoil table

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in 4-D.",
                                "Trefoil in 3-D.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Möbius-like cluster combined with a Gaussian.",
    "Multiple Gaussian clusters in high-dimensional space.",
    "Curvilinear cluster with a Gaussian cluster.",
    "K-link circular clusters (non-linear circular patterns).",
    "Chain-like circular clusters connected sequentially.",
    "K-link curvy cycle clusters (curvilinear loop structures).",
    "Chain-like curvy cycle clusters connected sequentially.",
    "Circular clusters with a Gaussian cluster in the middle.",
    "Curvy circular clusters with a Gaussian in the middle.",
    "Single grid in two dimensions.",
    "Two overlapping grids.",
    "Two grids shifted relative to each other.",
    "Parallel shaped clusters.",
    "Three clusters with different shapes. (eg:- 01, 02, ..., 20)")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

>>>>

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in $4\\text{-}D$.",
                                "Trefoil in $3\\text{-}D$.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para"), 
                        exp = c(
    "Möbius-like cluster combined with a Gaussian.",
    "Multiple Gaussian clusters in high-dimensional space.",
    "Curvilinear cluster with a Gaussian cluster.",
    "K-link circular clusters (non-linear circular patterns).",
    "Chain-like circular clusters connected sequentially.",
    "K-link curvy cycle clusters (curvilinear loop structures).",
    "Chain-like curvy cycle clusters connected sequentially.",
    "Circular clusters with a Gaussian cluster in the middle.",
    "Curvy circular clusters with a Gaussian in the middle.",
    "Single grid in two dimensions.",
    "Two overlapping grids.",
    "Two grids shifted relative to each other.",
    "Parallel shaped clusters.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```
